---
title: "Consulting"
output: 
  html_document:
    theme: cerulean
    code_folding: hide
---

```{r, message=FALSE, warning=FALSE} 
# Libraries
library(mosaic)
library(DT)
library(pander)
library(car)
library(tidyverse)
library(lattice)

# Data set
data <- read_csv("../Data/USBirths.csv")

# datatable(data)

# View(data)
```

# Backround

The number of births in the United States varies throughout the year due to various factors, such as seasonal changes, holidays, and cultural events. Understanding these patterns can provide valuable insights for healthcare planning, resource allocation, and policy-making. By analyzing the relationship between the time of year and the number of births, we can identify trends and make more informed decisions.

### Question

How does the day of the year influence the number of births in the United States?

## Hypotheses

\textbf{Hypotheses}

\textbf{Null Hypothesis} (\( H_0 \)):
\[
H_{0}: \beta_{\text{1}} = 0
\]

Null Hypothesis (H0):
The day of the year has no significant effect on the number of births in the United States.

\textbf{Alternative Hypothesis} (\( H_A \)):
\[
H_{A}: \beta_{\text{1}} \neq 0 \
\]
Alternative Hypothesis (H1):
The day of the year has a significant effect on the number of births in the United States.

\textbf{Significance level}
We will use a significance level of 0.05

### Regression Equation

Regression Equation
The simple linear regression equation is:
ð‘Œ=ð›½0+ð›½1ð‘‹

where:
ð‘ŒBirths is the predicted number of births,
ð›½0 is the y-intercept
ð›½1 is the slope of the regression line,
X is the independent variable representing the day of the year.

## Analysis

```{r, message=FALSE, warning=FALSE}
# Plot
# Plotting day of the year vs. births
plot <- ggplot(data, aes(x = day_of_year, y = births)) +
  geom_point(color = "blue", alpha = 0.6) +
  geom_smooth(method = "lm", se = FALSE, color = "red", linetype = "dashed") +
  labs(title = "Scatter Plot of Day of the Year vs. Number of Births",
       x = "Day of the Year",
       y = "Number of Births") +
  theme_minimal()

# Print the plot explicitly
print(plot)

# Fit linear regression model
model <- lm(births ~ day_of_year, data = data)

# Summary of the model
model_summary <- summary(model)

# Extract coefficients, R-squared, and p-value
coefficients <- coef(summary(model))
intercept <- coefficients[1, 1]
slope <- coefficients[2, 1]
r_squared <- model_summary$r.squared
p_value <- coefficients[2, 4]

# Display model summary in a table
model_summary_table <- data.frame(Intercept = intercept,
                                  Slope = slope,
                                  R_Squared = r_squared,
                                  P_Value = p_value)

pander::pander(model_summary_table)

```

## Numerical Summary

```{r, message=FALSE, warning=FALSE}
summary(data)

fivenum(data$day_of_year)

fivenum(data$births)
```

## Diagnostic Plots

```{r, message=FALSE, warning=FALSE}
par(mfrow = c(2, 2))
plot(model)
```

## Results and Interpretation 

The summary of the regression model provides several important pieces of information:

Intercept ð›½0: 228392
Slope ð›½1: 31.59
R-squared: 0.04698
P-value for slope:2.887e-05 

R-squared: The R-squared value of 0.04698 indicates that approximately 4.70% of the variability in the number of births is explained by the day of the year. This suggests a relatively weak linear relationship, implying that factors beyond the day of the year significantly influence birth rates in the United States.

p-value: The p-value for the slope is 2.887e-05, which is much less than the significance level of 0.05. This indicates that the relationship between the day of the year and the number of births is statistically significant, suggesting that there is a measurable effect of the day of the year on birth rates.

# Conclusion

These results indicate that there is a statistically significant relationship between the day of the year and the number of births in the United States. However, the R-squared value indicates that the day of the year explains only a small proportion of the variability in birth rates, highlighting the influence of other factors such as economic conditions, cultural practices, and healthcare policies on birth trends.